Manuscript draft

### 2019-06-19 manuscript/manuscript draft.Rmd
updated manuscript draft

*Which climatic variables are the most important drivers behind the latitudinal pattern in primary productivity?* All major carbon fluxes show similar responses to climate variables. Of the climate variables tested, annual wet days, aridity, cloud cover, mean diurnal temperature range and precipitation seasonality were poor explainers of variation in primary productivity, explaining less than 30% of the variation in each of the carbon fluxes.
We found that both measures of mean annual precipitation used were significant (p<0.05) but poor predictors of productivity, explaining at most 45% of variation in carbon flux. Despite being a poor predictor, the results indicate that there is a saturation point at between 3000 and 4000mm annual precipitation, above which productivity no longer increases.  
Looking across all productivity components, the climate variables which explain the highest amount of variation in carbon fluxes are temperature seasonality, mean annual temperature, annual temperature range, and vapour pressure. For measures of woody productivity (ANPP~woody~ and ANPP~woody stem~), potential evapotranspiration and vapour pressure deficit were also strong predictors.  
**Temperature seasonality**  
**Mean annual temperature**  
**Annual temperature range**  
**Vapour pressure**

>>>>

*Which climatic variables are the most important drivers behind the latitudinal pattern in primary productivity?* All major carbon fluxes show similar responses to climate variables. Of the climate variables tested, annual wet days, aridity, cloud cover, mean diurnal temperature range and precipitation seasonality were poor explainers of variation in primary productivity, explaining less than 30% of the variation in each of the carbon fluxes.
We found that both measures of mean annual precipitation used were significant (p<0.05) but poor predictors of productivity, explaining at most 45% of variation in carbon flux. Despite being a poor predictor, the results indicate that there is a saturation point at between 3000 and 4000mm annual precipitation, above which productivity no longer increases.  
Looking across all productivity components, the climate variables which explain the highest amount of variation in carbon fluxes are temperature seasonality, mean annual temperature, annual temperature range, and vapour pressure. For measures of woody productivity (ANPP~woody~ and ANPP~woodystem~), potential evapotranspiration and vapour pressure deficit were also strong predictors.

  ```{r echo=FALSE, out.width='100%', fig.cap = "Plots of primary productivity $(MgCha^-1^yr^-1^)$ regressed against the climate variables identified as the best predictors. Lines of best fit are plotted according to the best model selected during analysis. All regressions are significant $(p<0.05)$.", fig.pos='H'}
  knitr::include_graphics("combined_plots.png")
  ```

**Temperature seasonality**  
**Mean annual temperature**  
**Annual temperature range**  
**Vapour pressure**
